---
title: "Alcohol vs Seat choice"
author: "Daniela Olvera-Mota"
date: "Fall 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??

# Introduction

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.

$H_A$: There is a difference in the average number drinks consumed based on the row you sit in

# Methods

Alcohol ( response variable) is a numerical variable , Seat (explanatory variable) is a categorical variable. We will use the numerical~cat file.

## Results

### Graphical Results

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
This box plot shows the amount of alcohol consumed in the back seats, middle seats, and front seats. It shows how much alcohol consumed based on where you sit.The back seat people drank more than those in the middle seats and front seats.The middle and front seats consume about the same amount of alcohol, very little difference between them.

### get fancy


```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The back seat people drank more than those who sat in the front seats or middle seats.The people in the front seats and middle seats consumed about the same amount.

## Numerical Summary 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

This data shows the mean and median of the alcohol consumed by the people in the front,middle, and back seats.The data shows that the people in back seats drink at least three times more than the people in the front and middle seats.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The p value is 0.000116, which is less than 0.05.Therefore we would reject the null hypothesis which was that there was no difference in alcohol consumption based on seat you sit in.I can conclude that there is a difference in alcohol consumed based on what seat someone sits in.

```{r}
plot(TukeyHSD(model1))
```

We don't have evidence that there is a difference in the alcohol consumption between people in the front seats and middle seats. The only difference we found is that the back row consumes more alcohol than those in the front and middle seats

## Conclusions

The original question was is there a difference between the alcohol consumed between the row you choose to sit in? Yes, there is a difference between the alcohol consumed based on the seats chosen.

The p value was 0.000116, which is less than 0.05.Therefore we would reject the null hypothesis which was that there was no difference in alcohol consumption based on seat you sit in.I can conclude that there is a difference in alcohol consumed based on what seat someone sits in.


